Decomposing labelled proof theory for~intuitionistic~modal~logic

### 2020-08-31 FullyLabelled/JLC/system.tex
continue with reviews

Now we can present the inference rules for \emph{system $\labIKp$} for the logic $\IK$.
We obtained this system, shown in Figure~\ref{fig:labIKp}, as follows.
%\sonia{This is an interesting alternative view but for me the starting point really is the Maffezioli, Naibo and Negri paper. Maybe rephrase slightly to acknowledge their work too.}
Our starting point was the multiple-conlusion nested sequent system \emph{\`a la} Maehara (as presented in~\cite{str:2017maehara}), which can straightforwardly translated into the labelled setting, and which yields the rules $\llabrn\bot$, $\llabrn\AND$, $\rlabrn\AND$, $\llabrn\OR$, $\rlabrn\OR$, $\llabrn\DIA$, and $\rlabrn\DIA$ as we show them in Figure~\ref{fig:labIKp}. However, this naive translation would also yield the rules $\rn{id'}$, $\llabrn\IMP'$, and~$\llabrn\BOX'$:
\begin{equation}
  \label{eq:nomon}
  \vlinf{\rn{id}'}{}{\B, \Left, \labels{x}{a} \SEQ \Right, \labels{x}{a} }{}
  \quad
  \vliinf{\llabrn\IMP'}{}{\B,\Left, \labels{x}{A \IMP B} \SEQ \Right}{\B,\labels{x}{A \IMP B}, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left, \labels{x}{B} \SEQ \Right}
  \quad
  \vlinf{\llabrn\BOX}{}{\B, \accs xz, \Left, \labels{x}{\BOX A} \SEQ \Right}{\B, \accs xz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}
\end{equation}
that are not sufficient for a complete system, and we will see below
why. Before, let us first look at the rules $\rlabrn\IMP$ and
$\rlabrn\BOX$. In the multiple-conlusion nested sequent system
of~\cite{str:2017maehara}, these are the two rules that force
single-conclusion. 
%This is the reason why in our system we need the
%$\le$ in the relational atoms; we need to go to the future of the
%current world.  
%
In our system, this phenomenon is replaced by a re-positioning of the considered formulas to a fresh label.
%
In the Kripke-semantics in~\eqref{eq:kripke} the two
connectives $\IMP$ and $\BOX$ are the ones that make use of the
pre-order relation $\le$. This relation is reflexive and transitive. In
order to capture that in the proof system, we need to add the rules
$\rn{refl}$ and $\rn{trans}$.
%
These can be obtained by applying the axioms-as-rules methodology as in~\cite{maffezioli:etal:synthese13}.

@@

In the following sections, we will show that the system $\labIKp$ is sound and complete. For the completeness proof we proceed via cut elimination. The cut rule has the following shape:
\begin{equation}
  \label{eq:cut}
  \vliiinf{\labrn{cut}}{}{
    \lseq\B\Left\Right}{
    \lseq\B\Left{\Right,\labels{z}{C}}}{}{
    \lseq\B{\Left,\labels{z}{C}}{\Right}}
\end{equation}
Then we can summarize soundness, completeness, and cut
admissibility of $\labIKp$ in the following Theorem:

>>>>

Now we can present the inference rules for \emph{system $\labIKp$} for the logic $\IK$.
We obtained this system, shown in Figure~\ref{fig:labIKp}, as follows.
%\sonia{This is an interesting alternative view but for me the starting point really is the Maffezioli, Naibo and Negri paper. Maybe rephrase slightly to acknowledge their work too.}
Our starting point was the multiple-conlusion nested sequent system \emph{\`a la} Maehara (as presented in~\cite{str:2017maehara}), which can straightforwardly translated into the labelled setting, and which yields the rules $\llabrn\bot$, $\llabrn\AND$, $\rlabrn\AND$, $\llabrn\OR$, $\rlabrn\OR$, $\llabrn\DIA$, and $\rlabrn\DIA$ as we show them in Figure~\ref{fig:labIKp}. However, this naive translation would also yield the rules $\rn{id'}$, $\llabrn\IMP'$, and~$\llabrn\BOX'$:
\begin{equation}
  \label{eq:nomon}
  \vlinf{\rn{id}'}{}{\B, \Left, \labels{x}{a} \SEQ \Right, \labels{x}{a} }{}
  \quad
  \vliinf{\llabrn\IMP'}{}{\B,\Left, \labels{x}{A \IMP B} \SEQ \Right}{\B,\labels{x}{A \IMP B}, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left, \labels{x}{B} \SEQ \Right}
  \quad
  \vlinf{\llabrn\BOX}{}{\B, \accs xz, \Left, \labels{x}{\BOX A} \SEQ \Right}{\B, \accs xz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}
\end{equation}
that are not sufficient for a complete system, and we will see below
why. Before, let us first look at the rules $\rlabrn\IMP$ and
$\rlabrn\BOX$. In the multiple-conlusion nested sequent system
of~\cite{str:2017maehara}, these are the two rules that force
single-conclusion. 
%This is the reason why in our system we need the
%$\le$ in the relational atoms; we need to go to the future of the
%current world.  
%
In our system, this phenomenon is replaced by a re-positioning of the considered formulas to a fresh label.
%
\review{Also the proofs of the structural properties closely follow the methodology of the paper by Maffezioli, Naibo \& Negri. All this has to be said expressis verbis, and appropriate citations have to be added.}
\marianela{we are not saying that in the next paragraph?}
In the Kripke-semantics in~\eqref{eq:kripke} the two
connectives $\IMP$ and $\BOX$ are the ones that make use of the
pre-order relation $\le$. This relation is reflexive and transitive. In
order to capture that in the proof system, we need to add the rules
$\rn{refl}$ and $\rn{trans}$.
%
These can be obtained by applying the axioms-as-rules methodology as in~\cite{maffezioli:etal:synthese13}.

@@

\review{the authors of the paper under review neglect an important caveat in the design of rules of contraction-free labelled sequent calculi: to guarantee that contraction be admissible one needs to ensure that a certain closure condition be satisfied, see:

\emph{• Negri, S. Proof analysis in modal logic. Journal of Philosophical Logic, 34, 507–544, 2005.}}

\marianela{Should we mention Negri's paper here? }

\marianela{In the same way as we did with monotonicity, trying to avoid the problems that contraction has in a cut elimination proof, it is preferable to have a system in which this rule is admissible.
	\begin{remark}

		The rules $\llabrn{cont}$ and $\rlabrn{cont}$ are admissible for $\labIKp$.
		\begin{center}
			$\vlinf{\llabrn{cont}}{}{\B, \Left, \labels{x}{A} \SEQ \Right}{\B, \Left, \labels{x}{A}, \labels{x}{A} \SEQ \Right}$\quad\quad$\vlinf{\rlabrn{cont}}{}{\B, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left \SEQ \Right, \labels{x}{A}, \labels{x}{A}}$
		\end{center}
	\end{remark}
	\begin{proof}
		The rule $\llabrn{cont}$ can be derived using $\rn{refl}$ and $\llabrn{mon}$ which is admissible by Proposition 3.1.

		\begin{center}
			$\vlderivation{
				\vlin{\rn{refl}}{}
				{\B, \Left, \labels{x}{A} \SEQ \Right}
				{\vlin{\llabrn{mon}}{}
					{\B, \futs{x}{x}, \Left, \labels{x}{A} \SEQ \Right}
					{\vlhy{\B, \futs{x}{x}, \Left, \labels{x}{A}, \labels{x}{A} \SEQ \Right}}}
			}$
		\end{center}

		The case for $\rlabrn{cont}$ is similar.
	\end{proof}
	}
In the following sections, we will show that the system $\labIKp$ is sound and complete. For the completeness proof we proceed via cut elimination. The cut rule has the following shape:
\begin{equation}
  \label{eq:cut}
  \vliiinf{\labrn{cut}}{}{
    \lseq\B\Left\Right}{
    \lseq\B\Left{\Right,\labels{z}{C}}}{}{
    \lseq\B{\Left,\labels{z}{C}}{\Right}}
\end{equation}
Then we can summarize soundness, completeness, and cut
admissibility of $\labIKp$ in the following Theorem:
